The origin of cosmic-ray electrons in cluster outskirts

### 2012-01-18 paper.tex
update

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
%  \includegraphics[width=0.49\columnwidth]{./figures/CRespec0.3Rv.140.v12.eps}
%  \includegraphics[width=0.49\columnwidth]{./figures/CRespec1.4Rv.140.v12.eps}
  \caption{Cosmic ray electron spectra in cluster outskirts at
    redshift zero. We show the CR electron distribution function
    weighted with the electron Lorentz factor ($\gam_\e$)
    squared. In the {\it left panel} panel we show the CR electron in
    the region between (0.3-0.5)$\rvir$ and in the {\it right panel}
    between (1.3-1.5)$\rvir$. The solid lines show the median CR
    electron spectrum where both radiative and adiabatic losses are
    included. The dotted lines shows the 68 percentiles. The dashed
    lines show the CR electron spectrum without Coulomb and radiative
    cooling. Note that the Coulomb cooling at low energies is very
    inefficient because of the low electron densities in the cluster
    outskirts. \label{fig:e_spec}}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
%  \includegraphics[width=0.49\columnwidth]{./figures/f_evolution.0.3Rv.eps}
%  \includegraphics[width=0.49\columnwidth]{./figures/f_evolution.1.4Rv.eps}
  \caption{Time evolution of cosmic ray (CR) electron spectra. We show
    the CR electron distribution function weighted with the electron
    Lorentz factor ($\gam_\e$) squared. The time evolution of the CR
    electrons which at $z=0$ reside from (0.3-0.5)$\rvir$ are shown in
    the {\it left panel} and (1.3-1.5)$\rvir$ in the {\it right
      panel}. The black lines show the CR electrons with a
    $\gam_\e=30$, blue lines $\gam_\e=200$, and green lines
    $\gam_\e=10^4$. The solid lines show the CR electrons with full
    cooling, i.e. for Coulomb, inverse Compton, and adiabatic
    losses. Dashed lines show the CR electrons without Coulomb and
    inverse Compton cooling while the dash-dotted lines show the CR
    electrons without adiabatic cooling. The dotted line show the
    injected CR electron distribution function, derived from the
    injected CR protons. For each energy, we normalize the CR electron
    distribution function with the CR electrons without
    cooling. Notice that the high energy part is built up during the
    last Gyr. This is explained by the inverse Compton losses that are
    larger at high energies, especially at high redshifts where the
    energy density of the CMB is much larger than
    today.  \label{fig:e_evol}}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
%  \includegraphics[width=0.49\columnwidth]{./figures/evolution.0.3Rv.eps}
%  \includegraphics[width=0.49\columnwidth]{./figures/evolution.1.4Rv.eps}
  \caption{Time evolution of the gas density and the cosmic ray (CR)
    cooling time. We show the time evolution of the electron number
    density and CR electron cooling time that are associated with the
    CR electrons which at redshift $z=0$ reside from (0.3-0.5)$\rvir$
    in the {\it left panel} and (1.3-1.5)$\rvir$ in the {\it right
      panel}. The red lines show the electron number densities, where
    the dashed line show the median and dash-dotted the mean. The
    solid lines show the cooling times
    $\tau_\rmn{cool}=\gam_\e/[b_\IC(\gam_\e)+b_\rmn{C}(\gam_\e)]$
    for $\gam_\e=30$ (black), $\gam_\e=200$ (blue), and
    $\gam_\e=10^4$ (green). Interesting the CR cooling at low
    energies of the particles that end up in the center is constant
    while is increasing monotonically for the particles that end up in
    the cluster periphery. The density of the particles that end up in
    the center is roughly constant with time while it is decreasing
    for the particles that end up in the outer part. This is due to
    the expansion of the universe that counteract the contraction of
    the particles in the cluster periphery. \label{fig:evol}}
\end{minipage}
\end{figure*}

>>>>

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.32\columnwidth]{./figures/f_z.g72a.1.4Rv.a24.full.v20.eps}
  \includegraphics[width=0.32\columnwidth]{./figures/f_z.g1a.1.4Rv.a24.full.v20.eps}
  \includegraphics[width=0.32\columnwidth]{./figures/f_z.g676.1.4Rv.a24.full.v20.eps}
  \caption{NEEDS TO BE WRITTEN, WED}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.alphaCheck.eps}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.snapCheck.eps}
  \caption{NEEDS TO BE WRITTEN, WED}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{./figures/CRvolume.g72a.1.4Rv.a24.full.140.v20.eps}
  \includegraphics[width=0.49\columnwidth]{./figures/CRvolume.g1a.1.4Rv.a24.full.020.v20.eps}
  \caption{NEEDS TO BE WRITTEN, WED}
\end{minipage}
\end{figure*}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/CRespec.all.1.4Rv.a24.full.020.v20.eps}
  \caption{NEEDS TO BE WRITTEN, WED}
\end{figure}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/old/CRespecRadial.Radial2Rv.a24.140.v16.eps}
  \caption{replace figure with media all clusters, NEEDS TO BE WRITTEN, WED}
\end{figure}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/CRespec.g72a.1.4Rv.a24.full.140.v20.eps}
  \caption{NEEDS TO BE WRITTEN, WED\del{Cosmic ray electron spectra in
      cluster outskirts at redshift zero. We show the CR electron
      distribution function weighted with the electron Lorentz factor
      ($\gam_\e$) squared for a cluster with a recent merger for
      region between (1.3-1.5)$\rvir$. The solid lines show the median
      CR electron spectrum where both radiative and adiabatic losses
      are included. The dotted lines shows the 68 percentiles. The
      dashed lines show the CR electron spectrum without Coulomb and
      radiative cooling. Note that the Coulomb cooling at low energies
      is very inefficient because of the low electron densities in the
      cluster outskirts.}\label{fig:e_spec}}
\end{figure}

\del{
\begin{figure*}
\begin{minipage}{2.0\columnwidth}
%  \includegraphics[width=0.49\columnwidth]{./figures/CRespec0.3Rv.140.v12.eps}
%  \includegraphics[width=0.49\columnwidth]{./figures/CRespec1.4Rv.140.v12.eps}
  \caption{Cosmic ray electron spectra in cluster outskirts at
    redshift zero. We show the CR electron distribution function
    weighted with the electron Lorentz factor ($\gam_\e$)
    squared. In the {\it left panel} panel we show the CR electron in
    the region between (0.3-0.5)$\rvir$ and in the {\it right panel}
    between (1.3-1.5)$\rvir$. The solid lines show the median CR
    electron spectrum where both radiative and adiabatic losses are
    included. The dotted lines shows the 68 percentiles. The dashed
    lines show the CR electron spectrum without Coulomb and radiative
    cooling. Note that the Coulomb cooling at low energies is very
    inefficient because of the low electron densities in the cluster
    outskirts. \label{fig:e_spec}}
\end{minipage}
\end{figure*}
}

\del{
\begin{figure*}
\begin{minipage}{2.0\columnwidth}
%  \includegraphics[width=0.49\columnwidth]{./figures/f_evolution.0.3Rv.eps}
%  \includegraphics[width=0.49\columnwidth]{./figures/f_evolution.1.4Rv.eps}
  \caption{Time evolution of cosmic ray (CR) electron spectra. We show
    the CR electron distribution function weighted with the electron
    Lorentz factor ($\gam_\e$) squared. The time evolution of the CR
    electrons which at $z=0$ reside from (0.3-0.5)$\rvir$ are shown in
    the {\it left panel} and (1.3-1.5)$\rvir$ in the {\it right
      panel}. The black lines show the CR electrons with a
    $\gam_\e=30$, blue lines $\gam_\e=200$, and green lines
    $\gam_\e=10^4$. The solid lines show the CR electrons with full
    cooling, i.e. for Coulomb, inverse Compton, and adiabatic
    losses. Dashed lines show the CR electrons without Coulomb and
    inverse Compton cooling while the dash-dotted lines show the CR
    electrons without adiabatic cooling. The dotted line show the
    injected CR electron distribution function, derived from the
    injected CR protons. For each energy, we normalize the CR electron
    distribution function with the CR electrons without
    cooling. Notice that the high energy part is built up during the
    last Gyr. This is explained by the inverse Compton losses that are
    larger at high energies, especially at high redshifts where the
    energy density of the CMB is much larger than
    today.  \label{fig:e_evol}}
\end{minipage}
\end{figure*}
}

\del{
\begin{figure*}
\begin{minipage}{2.0\columnwidth}
%  \includegraphics[width=0.49\columnwidth]{./figures/evolution.0.3Rv.eps}
%  \includegraphics[width=0.49\columnwidth]{./figures/evolution.1.4Rv.eps}
  \caption{Time evolution of the gas density and the cosmic ray (CR)
    cooling time. We show the time evolution of the electron number
    density and CR electron cooling time that are associated with the
    CR electrons which at redshift $z=0$ reside from (0.3-0.5)$\rvir$
    in the {\it left panel} and (1.3-1.5)$\rvir$ in the {\it right
      panel}. The red lines show the electron number densities, where
    the dashed line show the median and dash-dotted the mean. The
    solid lines show the cooling times
    $\tau_\rmn{cool}=\gam_\e/[b_\IC(\gam_\e)+b_\rmn{C}(\gam_\e)]$
    for $\gam_\e=30$ (black), $\gam_\e=200$ (blue), and
    $\gam_\e=10^4$ (green). Interesting the CR cooling at low
    energies of the particles that end up in the center is constant
    while is increasing monotonically for the particles that end up in
    the cluster periphery. The density of the particles that end up in
    the center is roughly constant with time while it is decreasing
    for the particles that end up in the outer part. This is due to
    the expansion of the universe that counteract the contraction of
    the particles in the cluster periphery. \label{fig:evol}}
\end{minipage}
\end{figure*}
}
